Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-04-18 PaperDraft.Rmd

We would also like to look into statistical simulation models which consider intercity travel and geographic proximity. As our estimated $R$ is dependent on the serial interval number, it would also be worthwhile to see the sensitivity of our model with different values of serial interval number as did Flaxman et al. (2020)[6]. 
\newpage
# Appendix

@@

\begin{figure}
\includegraphics[width=.49\textwidth]{plots/plot2.png}
\includegraphics[width=.49\textwidth]{plots/plot3.png}
\includegraphics[width=.49\textwidth]{plots/plot4.png}
\end{figure}

$\lambda$ is an adjustment to the model based on the location. What we observe
from the distribution of $\lambda$ is that some locations have much more
certainty in how they deviate from the mean than others. This can be explained
by the unequal distribution of cases across provinces; provinces with more cases
lend themselves to more accurate estimation of $R$.

@@

\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot11.png}
\end{center}

This histogram shows all samples of all entries in the $\varepsilon$ matrix.
Generally, we prefer a lower average spread of $\varepsilon$, because it means
that more of the variation in reproduction number can be predicted from the
seasonal factors, location, and time alone. Unfortunately, we found the observed
spread of $\varepsilon$ is quite high, indicating that there is substantial
variance in reproductive numbers inferred from the data which cannot be
explained by modeled features.

>>>>

We would also like to look into statistical simulation models which consider intercity travel and geographic proximity. As our estimated $R$ is dependent on the serial interval number, it would also be worthwhile to see the sensitivity of our model with different values of serial interval number as did Flaxman et al. (2020)[6].

\newpage

# Appendix

@@

\begin{figure}
\centering
\includegraphics[width=.49\textwidth]{plots/plot2.png}
\includegraphics[width=.49\textwidth]{plots/plot3.png}
\includegraphics[width=.49\textwidth]{plots/plot4.png}
\caption{Posterior location of $\lambda$, split into three plots for each
location. $\lambda$ is an adjustment to the model based on the location.}
\end{figure}

What we observe from the distribution of $\lambda$ is that some locations have
much more certainty in how they deviate from the mean than others. This can be
explained by the unequal distribution of cases across provinces; provinces with
more cases lend themselves to more accurate estimation of $R$.

@@

\begin{figure}
\centering
\includegraphics[width=.49\textwidth]{plots/plot11.png}
\caption{Histogram of all samples of all entires in the $\varepsilon$ matrix.}
\end{figure}

Generally, we prefer a lower average spread of $\varepsilon$, because it means
that more of the variation in reproduction number can be predicted from the
seasonal factors, location, and time alone. Unfortunately, we found the observed
spread of $\varepsilon$ is quite high, indicating that there is substantial
variance in reproductive numbers inferred from the data which cannot be
explained by modeled features.
